Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-08-23 manuscripts/manuscript1_supplement.qmd
some mrs updates

>>>>

## mRS Data

```{r mrs90}

with_dir(here(), tar_load(m_posterior_mrs_90_canonical))

mod <- avg_predictions(m_posterior_mrs_90_canonical, by = "ich_laterality")

data <- mod |>
  select(group, ich_laterality, estimate) |>
  as_tibble() |>
  mutate(estimate = estimate * 100)

mrs_90 <- m_posterior_mrs_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

```{r mrs180}

with_dir(here(), tar_load(m_posterior_mrs_180_canonical))

data <- mod |>
  select(group, ich_laterality, estimate) |>
  as_tibble() |>
  mutate(estimate = estimate * 100)

mrs_180 <- m_posterior_mrs_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

mrs_180

```{r mrs365}

with_dir(here(), tar_load(m_posterior_mrs_365_canonical))

data <- mod |>
  select(group, ich_laterality, estimate) |>
  as_tibble() |>
  mutate(estimate = estimate * 100)

mrs_365 <- m_posterior_mrs_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

mrs_365

```{r euro anxiety}

with_dir(here(), tar_load(m_posterior_euro_anxiety_90_canonical))

euro_anxiety <- m_posterior_euro_anxiety_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

euro_anxiety

```{r euro mobility}

with_dir(here(), tar_load(m_posterior_euro_mobility_90_canonical))

euro_mobility <- m_posterior_euro_mobility_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

euro_mobility

```{r euro pain}

with_dir(here(), tar_load(m_posterior_euro_pain_90_canonical))

euro_pain <- m_posterior_euro_pain_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

euro_pain

```{r euro selfcare}
with_dir(here(), tar_load(m_posterior_euro_selfcare_90_canonical))

euro_selfcare <- m_posterior_euro_selfcare_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

euro_selfcare

```{r euro usual}
with_dir(here(), tar_load(m_posterior_euro_usual_90_canonical))

euro_usual <- m_posterior_euro_usual_90_canonical |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  summarize(
    or_1 = sum(ich_right_or > 1) / n(),
    or_1.1 = sum(ich_right_or > 1.1) / n(),
    or_1.2 = sum(ich_right_or > 1.2) / n(),
    rope = sum(ich_right_or < 1.05 & ich_right_or > 0.95) / n()
  )

euro_usual
